Joint analysis of read count data

### 2020-09-04 combined_analysis/combine_all_data.Rmd
Fix Dx

# SCZ by sex
L_SCZ = Lbase
L_SCZ['DxSCZ:Reported_GenderMale'] = 1
L_SCZ['Reported_GenderMale'] = -1
L_SCZ['DxSCZ'] = -1
L_SCZ['DxControl'] = 1 
# (A - B) - (C - D) = A - B - C + D

# BP by sex
L_BP = Lbase
L_SCZ['DxBP:Reported_GenderMale'] = 1
L_SCZ['Reported_GenderMale'] = -1
L_SCZ['DxBP'] = -1
L_SCZ['DxControl'] = 1

@@

fit_interaction_DxSex = dream(vobj, form, METADATA, L=L,BPPARAM = SnowParam(18))
```

>>>>

# BP by sex
L_BP = Lbase
L_SCZ['Reported_GenderMale'] = 1
L_SCZ['DxControl:Reported_GenderMale'] = -1
L_SCZ['DxBP'] = -1
L_SCZ['DxControl'] = 1

@@

fit_interaction_DxSex = dream(vobj, form, METADATA, L=L, BPPARAM = SnowParam(18))
```
